TacticToe: Learning to Prove with Tactics

### 2018-03-27 tactictoe_jv.tex
minor line breaks
ldots in figure

\lstdefinelanguage{SMLSmall}%
{columns=fullflexible,
  keywords={THEN,THENL,val,open,store_thm,fun,fn,let,in,end,true,
  while,do,if,then,else,break,return,;},%
  frame=none,
  sensitive=true,
  keywordstyle=\fontfamily{lmss}\scriptsize\selectfont,%
  basicstyle=\fontfamily{pcr}\small\selectfont,%
  stringstyle=\tt,
  morestring=[b]",
  literate={\ }{$\mkern6mu$}1%
   {=}{{\tt\raisebox{-.15mm}{=}}}1%
   {[}{{\tt\raisebox{-.15mm}{[}}}1%
   {]}{{\tt\raisebox{-.15mm}{]}}}1%
   {->}{{$\rightarrow$}}1%
   {==>}{{$\Rightarrow$}}1%
   {wedge}{{$\wedge$}}1%
   {<=}{{$\leq$}}1%
   {>=}{{$\geq$}}1%
   {'a}{{$\alpha$}}1%
   {'b}{{$\beta$}}1%
   {ldots}{$\ldots$}1%
   {emptyset}{$\emptyset$}1%
   {!}{$\forall$}1%
   {fff}{{DB.fetch}}1%
   {``}{\hspace{-.5mm}`\hspace{-1mm}`}1%
  }
\lstset{language=SML}
\begin{document}
\maketitle

@@

\begin{figure}{}
\begin{center}
\begin{tikzpicture}[node distance=0.7cm]
\node [tcircle] (0) {$g_i$};
\node [right of=0] (0r) {.\ .\ .};
\node [tcircle,right of=0r] (0rr) {$g_n$};
\node [left of=0] (0l) {.\ .\ .};
\node [tcircle,left of=0l] (0ll) {$g_0$};
\node [draw,fit=(0rr) (0ll)] (0b) {};
\node [left of=0ll] {$a_0$};
\node [above of=0,node distance=2cm] (2) {.\ .\ .};
\node [left of=2, tcircle] (2l) {$\phantom{g_3}$};
\node [tcircle,right of=2] (2r) {$\phantom{g_3}$};
\node [draw, fit=(2l) (2r)] (2b) {};
\node [left of=2l] {$a_j$};

\node [tcircle, left of=2l, node distance=3cm] (1r) {$\phantom{g_3}$};
\node [left of=1r] (1) {.\ .\ .};
\node [tcircle, left of=1] (1l) {$\phantom{g_3}$};
\node [draw, fit=(1l) (1r)] (1b) {};
\node [left of=1l] {$a_1$};

\node [right of=2r,node distance=3cm] (3l) {$\phantom{g_3}$};
\node [right of=3l] (3) {\phantom{.\ .\ .}};
\node [right of=3] (3r) {$\phantom{g_3}$};
\node [fit=(3l) (3r)] (3b) {};

@@

\section{Minimization and Embellishment}\label{sec:proofdisplay}

When \tactictoe finds a proof of an initial goal, it returns a search tree
$\mathfrak{T}$ where the root node containing the initial goal is solved.
In order to transform this search tree into a tactic proof, we need to extract
the tactics that contributed to the proof and combine them using tactic
combinators.

>>>>

\lstdefinelanguage{SMLSmall}%
{columns=fullflexible,
  keywords={THEN,THENL,val,open,store_thm,fun,fn,let,in,end,true,
  while,do,if,then,else,break,return,;},%
  frame=none,
  sensitive=true,
  keywordstyle=\fontfamily{lmss}\scriptsize\selectfont,%
  basicstyle=\fontfamily{pcr}\small\selectfont,%
  stringstyle=\tt,
  morestring=[b]",
  literate={\ }{$\mkern6mu$}1%
   {=}{{\tt\raisebox{-.15mm}{=}}}1%
   {[}{{\tt\raisebox{-.15mm}{[}}}1%
   {]}{{\tt\raisebox{-.15mm}{]}}}1%
   {->}{{$\rightarrow$}}1%
   {==>}{{$\Rightarrow$}}1%
   {wedge}{{$\wedge$}}1%
   {<=}{{$\leq$}}1%
   {>=}{{$\geq$}}1%
   {'a}{{$\alpha$}}1%
   {'b}{{$\beta$}}1%
   {ldots}{$\ldots$}1%
   {emptyset}{$\emptyset$}1%
   {!}{$\forall$}1%
   {fff}{{DB.fetch}}1%
   {``}{\hspace{-.5mm}`\hspace{-1mm}`}1%
  }
\lstset{language=SML}

\begin{document}
\maketitle

@@

\begin{figure}{}
\begin{center}
\begin{tikzpicture}[node distance=0.7cm]
\node [tcircle] (0) {$g_i$};
\node [right of=0] (0r) {...};
\node [tcircle,right of=0r] (0rr) {$g_n$};
\node [left of=0] (0l) {...};
\node [tcircle,left of=0l] (0ll) {$g_0$};
\node [draw,fit=(0rr) (0ll)] (0b) {};
\node [left of=0ll] {$a_0$};
\node [above of=0,node distance=2cm] (2) {...};
\node [left of=2, tcircle] (2l) {$\phantom{g_3}$};
\node [tcircle,right of=2] (2r) {$\phantom{g_3}$};
\node [draw, fit=(2l) (2r)] (2b) {};
\node [left of=2l] {$a_j$};

\node [tcircle, left of=2l, node distance=3cm] (1r) {$\phantom{g_3}$};
\node [left of=1r] (1) {...};
\node [tcircle, left of=1] (1l) {$\phantom{g_3}$};
\node [draw, fit=(1l) (1r)] (1b) {};
\node [left of=1l] {$a_1$};

\node [right of=2r,node distance=3cm] (3l) {$\phantom{g_3}$};
\node [right of=3l] (3) {\phantom{...}};
\node [right of=3] (3r) {$\phantom{g_3}$};
\node [fit=(3l) (3r)] (3b) {};

@@

\section{Minimization and Embellishment}\label{sec:proofdisplay}
When \tactictoe finds a proof of an initial goal, it returns a search tree
$\mathfrak{T}$ where the root node containing the initial goal is solved.
In order to transform this search tree into a tactic proof, we need to extract
the tactics that contributed to the proof and combine them using tactic
combinators.
